How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-29 Manuscript.tex
Updates from ShareLaTeX

An  interesting feature of \fig{changed} was that fewer things 
were changed in the Seigmund data sets like {\em BDBJ} than in the Jureczko data set like
{\em lucene}. 
In turns out that this holds true across nearly all our data sets.
\fig{types} summarizes all the change frequencies for all data sets. As with  \fig{changed},
there are fewer changed features in the Seigmund data than in the defect prediction data. 
One explanation for that is the nature of the features: the
Jureczko data sets have continuous
features while the 
Seigmund data has binary independent features (where settings can be turned ``ON'' or ``OFF''). While the features of the Jureczko data sets are not constrained, those of Seigmund data sets are subject to several constrains (dictated by their feature models, see \fig{bdbc}). It is possible that planners in Method1, Method2, and Method3 find very few valid settings that can improve the performance scores, thereby making insignificant changes. As evidenced by the results in \fig{}

@@

If a planner only ever reports conclusions that were already known, then that planner offers
little value over ``just use established wisdom''. Accordingly, we studied our results
for plans that were somewhat counter-intuitive.

Such a surprising plan can be  seen in the {\em lucene} results. Recall the standard advice for
OO systems: build classes that are internally cohesive with low coupling to other parts of the system~\cite{Dhama199565}. We can assess the relevance of this advice
to specific projects by checking how often a planner changes the
 coupling-related features:
\bi
\item {\em ca}:   afferent couplings  =  \# classes using this
				class;
\item {\em  	ce}:  efferent couplings =  \# classes  used by this
				  class. 
\item {\em cbm}: coupling between methods =  \# new/redefined methods
				to which all the inherited methods are coupled
\item	{\em cbo}:  coupling between objects = a value that increases when the methods of one
				class access services of another.

\item {\em ic}:   inheritance coupling =  \# parent classes  which a given
				class is coupled (includeing methods and variables inherited)
\ei
In many of our results with the Jureczko data, it was indeed true that the changes
proposed by XTREE lead to lower coupling. However, the {\em lucene} results were quite
different and quite surprising.

In the {\em lucene} XTREE results  of  \fig{changed},
the most frequent change was to alter the lines of code in a class (see the tallest
red historgram in that figure on the {\em loc}, or lines of code). 
Looking at the logs of our planner, we can see
that XTREE's proposed change is to {\em reduce} the size of a class.
The only way to do that,  while keeping the  same functionality, is to create a network
of smaller classes that interact to produce that functionality.
That is, we would need to {\em increase} the coupling of those classes to achieve XTREE's plan.

@@

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:
\bi
\item All our planners divide data into groups of size $\alpha=\sqrt{N}$
\item Method2 used the top $\beta=33\%$ most informative features (ranked using INFOGAIN);
\item Method3 uses  $\omega=0.5$ to find its deltas;
\item XTREE considered a sibling useful if it's score was less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei

>>>>

An  interesting feature of \fig{changed} was that fewer things 
were changed in the Seigmund data sets like {\em BDBJ} than in the Jureczko data set like
{\em lucene}. 
In turns out that this holds true across nearly all our data sets.
\fig{types} summarizes all the change frequencies for all data sets. As with  \fig{changed},
there are fewer changed features in the Seigmund data than in the defect prediction data. 
One explanation for that is the nature of the features: the
Jureczko data sets have continuous
features while the 
Seigmund data has binary independent features (where settings can be turned ``ON'' or ``OFF''). While the features of the Jureczko data sets are not constrained, those of Seigmund data sets are subject to several constrains (dictated by their feature models, see \fig{bdbc}). It is possible that planners in Method1, Method2, and Method3 find very few valid settings that can improve the performance scores, thereby making insignificant changes. As a result all methods, except XTREE, fail to optimize the runtime, as evidenced by the results in \fig{conf1}.

@@

If a planner only ever reported conclusions that were already known, then that planner offers
little value over ``just use established wisdom''. Accordingly, we studied our results
for plans that were somewhat counter-intuitive.

Such a surprising plan can be  seen in {\em lucene}. Recall the standard advice for
OO systems: build classes that are internally cohesive with low coupling to other parts of the system~\cite{Dhama199565}. We can assess the relevance of this advice
to specific projects by checking how often a planner changes the
 coupling-related features:
\bi
\item {\em ca}:   afferent couplings  =  \# classes using this
				class;
\item {\em  	ce}:  efferent couplings =  \# classes  used by this
				  class. 
\item {\em cbm}: coupling between methods =  \# new/redefined methods
				to which all the inherited methods are coupled
\item	{\em cbo}:  coupling between objects = a value that increases when the methods of one
				class access services of another.

\item {\em ic}:   inheritance coupling =  \# parent classes  which a given
				class is coupled (includeing methods and variables inherited)
\ei
In many of our results with the Jureczko data, it was indeed true that the changes
proposed by XTREE lead to lower coupling. However, the {\em lucene} results were quite
different and rather surprising.

In the {\em lucene} XTREE results  of  \fig{changed},
the most frequent change was to alter the lines of code in a class (see the tallest
red histogram in that figure on the {\em loc}, or lines of code). 
Looking at the logs of our planner, we can see
that XTREE's proposed change is to {\em reduce} the size of a class.
The only way to do that,  while keeping the  same functionality, is to create a network
of smaller classes that interact to produce that functionality.
That is, we would need to {\em increase} the coupling of those classes to achieve XTREE's plan.

@@

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:
\bi
\item All our planners divide data into groups of size $\alpha=\sqrt{N}$;
\item Method2 used the top $\beta=33\%$ most informative features (ranked using INFOGAIN);
\item Method3 uses  $\omega=0.5$ to find its deltas;
\item XTREE considered a sibling useful if it's score was less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei
